\documentclass[../DoAn.tex]{subfiles}
\begin{document}
\begin{enumerate}[label={[\arabic*]}, leftmargin=1.5cm]
    \item Binance Smart Chain, Available: \url{https://docs.bnbchain.org/}. (visited on 01/05/2025).
    \item Ethereum Virtual Machine, Available: \url{https://ethereum.org/en/developers/docs/evm/}. (visited on 01/05/2025).
    \item Solidity, Available: \url{https://docs.soliditylang.org/}. (visited on 01/05/2025).
    \item ERC-721 Non-Fungible Token Standard, Available: \url{https://eips.ethereum.org/EIPS/eip-721}. (visited on 01/05/2025).
    \item MetaMask, Available: \url{https://docs.metamask.io/}. (visited on 01/05/2025).
    \item TypeScript, Available: \url{https://www.typescriptlang.org/docs/}. (visited on 01/05/2025).
    \item Node.js, Available: \url{https://nodejs.org/en/docs/}. (visited on 01/05/2025).
    \item NestJS, Available: \url{https://docs.nestjs.com/}. (visited on 01/05/2025).
    \item React, Available: \url{https://react.dev/}. (visited on 01/05/2025).
    \item Next.js, Available: \url{https://nextjs.org/docs}. (visited on 01/05/2025).
    \item PostgreSQL, Available: \url{https://www.postgresql.org/docs/}. (visited on 01/05/2025).
    \item Redis, Available: \url{https://redis.io/docs/}. (visited on 01/05/2025).
    \item Amazon S3, Available: \url{https://docs.aws.amazon.com/s3/}. (visited on 01/05/2025).
    \item JSON Web Token, Available: \url{https://jwt.io/}. (visited on 01/05/2025).
    \item Sign-In with Ethereum, Available: \url{https://login.xyz/}. (visited on 01/05/2025).
    \item Docker, Available: \url{https://docs.docker.com/}. (visited on 01/05/2025).
    \item Ethers.js, Available: \url{https://docs.ethers.org/}. (visited on 01/05/2025).
    \item OpenZeppelin, Available: \url{https://docs.openzeppelin.com/}. (visited on 01/05/2025).
    \item Modular Monolith Architecture, Available: \url{https://www.geeksforgeeks.org/system-design/what-is-a-modular-monolith/}. (visited on 01/05/2025).
    \item RESTful API, Available: \url{https://restfulapi.net/}. (visited on 01/05/2025).
\end{enumerate}


\end{document}